Probabilistic Programming

### 2014-04-21 paper/paper.tex
Discuss alternative IDE approaches

\begin{figure}[h]
  \centering
  \includegraphics[width=0.90\textwidth]{screenshot}
  \caption{Screenshot of the web program editor GUI} \label{fig:screenshot}
\end{figure}

@@

This is a limitation of the current model, that identifier names are chosen
probabilistically based on their position in the code, without regard to whether
they are in scope and without refering to anything in another part of the
program.

\subsection{Limitations of the IDE}

Usability issues

@@

Choosing valid identifiers, matching identifiers

>>>>

\begin{figure}[h]
  \centering
  \includegraphics[width=1.00\textwidth]{screenshot}
  \caption{Screenshot of the web program editor GUI} \label{fig:screenshot}
\end{figure}

@@

This is a limitation of the current model, that identifier names are chosen
probabilistically based on their position in the code, without regard to whether
they are in scope and without refering to anything in another part of the
program. Because of this limitation, the Guided IDE is not useful for practical
purposes. We consider some alternative approaches for the Guided IDE using a
similar model.

\subsection{Alternative approaches for the IDE}

\subsubsection{Prompt for identifiers}

Rather than picking identifier names from the model, use placeholder identifiers
and prompt the user to enter actual identifiers, with suggestions based on the
current variables in scope and previously used identifiers. This would give the
user the opportunity to create semantically valid programs, but the entering of
identifier names could be tedious.

\subsubsection{Stubs}

Instead of having a movable cursor in the code window, have stubs in the
program. Each stub would be a marker in place of an AST node. The user would
select a stub and be given choices of snippets to replace it. Selecting a
snippet would move the current snippet into the program in place of the selected
stub.  The generated snippets could themselves have stubs in them, so that the
user may continue to complete stubs and expand their program.  At the level of
variable identifiers, the snippet suggestions would be taken from the computed
list of in-scope variables at the position of the selected stub, unless the
completion was for a variable declaration, in which case the user would be
prompted to name a new variable.

This approach, while offering less places to insert code then the current
approach, would allow for programs to more closely be generated from our model,
since the stub completions would always be at leaf nodes of the AST, whereas in
the current approach the user may choose to insert a snippet in the middle of a
list, which means that the transition from the inserted snippet to the following
node in the list does not in general follow from the model.

While the stub approach would be more restrictive for the user as it requires
them to build the program in a certain way, with proper handling of identifiers,
it may provide for an interesting or useful paradigm for interacting with a program
source.

%\subsection{Limitations of the IDE}

@@

\subsection{Extending the model}

%Choosing valid identifiers, matching identifiers
